Natural variation in teosinte at the domestication locus teosinte branched1 (tb1)

### 2014-05-13 manuscript.tex
edits
updated to do list for LV
fixed numbers in tables

%TO DO
%Fix figures and tables
%add usepackage for tables
%check citations in last paragraph for term
%reformat for journal
%finish fixing paragraph that jeff doesn't like

@@

 % Table 4 Assigment to maize and teosinte in tb1 region and chr 1 
\begin{table}[htbp]
  \centering
  \caption{Assignments to maize and teosinte in the \emph{tb1} and chromosome 1 regions from STRUCTURE}
    \begin{tabular}{ccccc}
  %  \toprule
          & \multicolumn{2}{c}{\emph{tb1} region} & \multicolumn{2}{c}{Chr 1} \\
 %   \midrule
    Population & Maize assignment & Teosinte assignment & Maize assignment & Teosinte assignment \\
    Ejutla A & 0.02158681 & 0.9784132 & 0.2026814 & 0.7973186 \\
    Ejutla B & 0.01888194 & 0.9811181 & 0.1872131 & 0.8127869 \\
    La Mesa & 0.9881333 & 0.0118675 & 0.8068998 & 0.1931017 \\
    San Lorenzo & 0.01551389 & 0.9844861 & 0.2048252 & 0.7951748 \\
 %   \bottomrule
    \end{tabular}
  \label{Table4Q}
\end{table}

>>>>

%TO DO
%Fix figures and tables
%add usepackage for tables
%check citations in last paragraph for ter1
%reformat for AJB
%preprint somewhere
%finish fixing paragraph that jeff doesn't like
%check map details
%make figs smaller so they don't go to end of document
%Code for SAS and command line stuff on Git
%Phenotyping and genotyping data on Git (it's on Figshare?)

@@

 % Table 4 Assigment to maize and teosinte in tb1 region and chr 1 
\begin{table}[htbp]
  \centering
  \caption{Assignments to maize and teosinte in the \emph{tb1} and chromosome 1 regions from STRUCTURE}
    \begin{tabular}{ccccc}
  %  \toprule
          & \multicolumn{2}{c}{\emph{tb1} region} & \multicolumn{2}{c}{Chr 1} \\
 %   \midrule
    Population & Maize assignment & Teosinte assignment & Maize assignment & Teosinte assignment \\
    Ejutla A & 0.02158681 & 0.9784132 & 0.2026814 & 0.7973186 \\
    Ejutla B & 0.01888194 & 0.9811181 & 0.1872131 & 0.8127869 \\
    La Mesa & 0.0118675 & 0.9881333 & 0.8068998 & 0.1931017 \\
    San Lorenzo & 0.01551389 & 0.9844861 & 0.2048252 & 0.7951748 \\
 %   \bottomrule
    \end{tabular}
  \label{Table4Q}
\end{table}
